\LARGE \bf Sandhi: An open source alternative to LabVIEW

### 2014-01-19 paper.tex
Added New Flow graphs, graphs, references

\subsection{Simulation Capabilities}
The functions chosen to illustrate Sandhi¿s simulation capabilities are following:
\begin{itemize}
\item csim - used for generating continuous time response of linear systems.
\item dsim - used for generating discrete time response of linear systems.
\end{itemize}
The following screenshots demonstrate simulations in Sandhi

@@

	\bibitem{c1} GNU Radio- The Free \& Open Software Radio Ecosystem- Blocks Coding guide in C++ and tutorials for writing Python Application http://gnuradio.org/redmine/projects/gnuradio/wiki/BlocksCodingGuide
	\bibitem{c2} Virtual Labs initiative http://en.wikipedia.org/wiki/Virtual\_Labs\_(India) 
	\bibitem{c3} Inderpreet Arora, Kannan M. Moudgalya, Kaushik Venkata, Victor Chakraborty, Rupak Rokade and Rakhi R., A Low Cost, Scalable, Virtual Control Laboratory, Santiago, Chile, IEEE Conference on Control and Automation.
	\bibitem{c4} Sciscipy: Scilab API for Python http://forge.scilab.org/index.php/p/sciscipy
	\bibitem{c5} Linux on Aakash tablet https://github.com/androportal/linux-on-aakash
	\bibitem{c6} GNU Radio Advanced Scheduler, developed by Josh Blum, Ettus Resarch, https://github.com/guruofquality/gras
	\bibitem{c7} GNU Radio Python blocks Writing python blocks https://github.com/aviralchandra/gr-py\_block
	\bibitem{c8} Jagdish Y. Patil, Balashish Dubey, Kannan M. Moudgalya, Rakesh Peter: GNU Radio, Scilab, Xcos and COMEDI for Data Acquisition and Control: An Open Source Alternative to LabVIEW, Article, IIT Bombay, Mumbai 400076
	\bibitem{c9} Dictino Chaos1;*, Jes  ¿us Chac ¿on1, Jose Antonio Lopez-Orozco2 and Sebasti ¿an Dormido1 : Virtual and Remote Robotic Laboratory Using EJS, MATLAB and LabVIEW
	\bibitem{c10} Kannan M. Moudgalya. Digital Control. John Wiley and Sons, 2009
	\bibitem{c11} Scilab, open source software for numerical computation, www.scilab.org
\end{thebibliography}

>>>>

\subsection{Simulation Capabilities}
The functions chosen to illustrate Sandhi¿s simulation capabilities are following:
\begin{itemize}
\item csim - used for generating continuous time response of linear systems.
\item dsim - used for generating discrete time response of linear systems.
\end{itemize}
The following screenshots demonstrate simulations in Sandhi-

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{csim_open.png}
	\caption{Open loop continuous time simulation flow graph}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{step_response.png}
	\caption{Step response plot for open loop csim block}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{dsim_closed.png}
	\caption{Open loop discrete time simulation flow graph}
	\label{overflow}
\end{figure}

@@

	\bibitem{c1} GNU Radio- The Free \& Open Software Radio Ecosystem- Blocks Coding guide in C++ and tutorials for writing Python Application http://gnuradio.org/redmine/projects/gnuradio/wiki/BlocksCodingGuide
	\bibitem{c2} Virtual Labs initiative http://en.wikipedia.org/wiki/Virtual\_Labs\_(India) 
	\bibitem{c3} Inderpreet Arora, Kannan M. Moudgalya, Kaushik Venkata, Victor Chakraborty, Rupak Rokade and Rakhi R., A Low Cost, Scalable, Virtual Control Laboratory, Santiago, Chile, IEEE Conference on Control and Automation.
	\bibitem{c4} Sciscipy: Scilab API for Python http://forge.scilab.org/index.php/p/sciscipy
	\bibitem{c5} Linux on Aakash tablet https://github.com/androportal/linux-on-aakash
	\bibitem{c6} GNU Radio Advanced Scheduler, developed by Josh Blum, Ettus Resarch, https://github.com/guruofquality/gras
	\bibitem{c7} GNU Radio Python blocks Writing python blocks https://github.com/aviralchandra/gr-py\_block
	\bibitem{c8} Jagdish Y. Patil, Balashish Dubey, Kannan M. Moudgalya, Rakesh Peter: GNU Radio, Scilab, Xcos and COMEDI for Data Acquisition and Control: An Open Source Alternative to LabVIEW, Article, IIT Bombay, Mumbai 400076
	\bibitem{c9} Dictino Chaos, Jesus Chacon, Jose Antonio Lopez-Orozco and Sebastian Dormido : Virtual and Remote Robotic Laboratory Using EJS, MATLAB and LabVIEW
	\bibitem{c10} Kannan M. Moudgalya, "Proportional, Integral, Derivative Controllers" in Digital Control, Chichester, U.K., Wiley, 2007, pp. 301-319
	\bibitem{c11} Scilab, open source software for numerical computation, http://www.scilab.org
	\bibitem{c12} Dale E. Seborg, Thomas F. Edgar, Duncan A. Mellichamp, "Feedback Controllers" in Process Dynamics and Control, Second Edition, Hoboken, NJ, Wiley, 2004, pp. 185-200
\end{thebibliography}
